Make any stupid plot you want

### 2020-09-25 draft/intro.tex
setting up symmetry tables

\subsection{What is the artist}
Visualization is a two step process where the artists $A$ transforms the data into visual encodings $V$ and then the renderer $R$ transfroms the encodings $V$ to the set of pixels in $P$.
\begin{equation}
    \label{eq:artist}
    A: D \mapsto V
\end{equation}

\begin{equation}
    \label{eg:renderer}
    R: V \mapsto P
\end{equation}

>>>>

\subsection{What is the artist}
Visualization is a two step process where the artists $A$ transforms the data into visual encodings $V$ and then the renderer $R$ transfroms the encodings $V$ to the set of pixels in $P$.
\begin{equation}
    \label{eq:artist}
    A: D \mapsto M
\end{equation}
TYPES: A(D) = M
Spivak A is analogous DT

D is the type  which means it's indexexer K(M/indexer) + V (fiber bundle)
d is a section of a bundle is the data is the values given keys on m + vars on V (c in C)
a(d) = M

$M$ is a composition of the visual channels applied as ....
Is also a CW/simplicial complex/simplacial set

Channels are ducktyping the variable types
Marks are encoding seperability

Marks are mapping of simplacial complex into RGB space

(find paper on complex marks)

for every key value in M, have coordinates in the fiber (space)
section: keys -> values

Scatter Plot:
K - 0D disconnected points

A: (C1, C2, C3...)\mapsto (M....)
t \in A
-> preserve type operation and relation

M is the disjoint collection of the output of all these transformers where the transformers preserve the relation and order. M is a bunch of disconnected Marks

Line Plot:
L - 1D, can be a function on an interval [a,b]
functions in the column...f(key) -> values

invariance: \mapto -> preserves operations/relations types
K might have symmetry -> move back and forth in time, preserved in K
symmatry in fibers -> scaled up/down, categorical,
preserved in the visual variables

groups on K and fibers and subgroups w/ different types and temperatures (Steven's fundemental data types-measurment scales and types)

intervals can transalte, ratio can only scale
group of fibers has to do w/ measurment types
channels themselves independent of data have their own symmatery

(make table of what symmateries are preserved)
visual transformation groups

instead of inputting parameter into input, get to all the other parameters - base thing is a square, 
preserved: operation(D) <-> operation (M)
if A(g*d) = A(d)*g

normalizations of scales in mpl - devision usually leaves same picture but axis is affected - visually length got uniformally smaller but we changed ticks to compensate
Axes has rules about how transform affects it - inside graph invariance is preserved

groups:
symmteries of K
symmetries of cartesian product of columns
each visual channel has symmtery group associated w/
orbit- space of possible visualiztions by changing the constants of each aesthetic (or f_{red}->f_{green})  
visual type might be orbit of that (orbit of function in space)->single function that can be transformed in that way
each visualization type is an orbit & then try to set up equivalence on these...

artist will respect that w/ equivariance, knob on one side will tweak knob on another

\begin{table}
    \begin{tabular}{|r|r|}

    \end{tabular}
\caption{Symmetrys one the data preserved with each type of mark\cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}}
\label{tab:symmetry_mark}
\end{table}

\begin{table}
\begin{tabular}{|r|r|}

\end{tabular}
\caption{Symmetries on variable columns C \caption{Symmetrys one the data preserved with each type of channel \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}}
\label{tab:symmetry_channel}
\end{table}
Combining 
\begin{equation}
    \label{eg:renderer}
    R: M \mapsto P
\end{equation}
Where $P$ is the set of pixels rendered to screen ${p_{i,j} \in P}$
